---
title: "Tidy Template"
author: "Fabio Votta"
date: "The Date"
output: html_document
---

This script is about:

Analyzing retaliatory tariffs

## Packages and Folders

```{r}
# Install these packages if you don't have theme yet
# devtools::install_github("favstats/tidytemplate")
# install.packages("pacman")

pacman::p_load(tidyverse, httr, janitor, urbnmapr, glue, ggthemes, tidytemplate)

# Creates folders
# tidytemplate::data_dir()
# tidytemplate::images_dir()
```


## Get Brrokings Data

```{r, data}

brookings_url <- "https://www.brookings.edu/wp-content/uploads/2018/09/2018.10.04_Metro_dataappendix_tariffs.xlsx"

GET(brookings_url, write_disk(tf <- tempfile(fileext = ".xlsx")))

tariff_data <- read.xlsx(tf, sheetName = "Areas", startRow = 3) %>% 
  clean_names() %>% 
  select(-na:-na_2) %>% 
  rename(CBSA = fips) %>% 
  drop_na(CBSA)

tidytemplate::save_it(tariff_data)
```

## Merging with County Data

```{r}
tariff_data <- tariff_data %>% 
  inner_join(totalcensus::dict_cbsa %>% 
              mutate(county_fips = paste0(STATE, COUNTY)) %>% 
              select(CBSA, central_outlying, county_fips)) %>% 
  group_by(county_fips) %>% 
  summarise_at(vars(total_exports_mil:total_export_supported_jobs_under_retaliation), sum)

#%>% 
  left_join(urbnmapr::counties)  %>% 
  ggplot(aes(long, lat, group = group, fill = direct_export_supported_jobs)) +
  geom_polygon(color = NA) +
  coord_map() +
  labs(fill = "Number of Refugees") +
  theme_map() +
  viridis::scale_fill_viridis("Number of Refugees", 
                              direction = -1,
                              option = "D")  +
  labs(x = "", y = "",
       title = "Refugees arriving in the United States of America (2002 - 2018)",
       caption = "Data: Department of State, Office of Admissions - Refugee Processing Center   \nTotal accepted Refugees in Timerange: 943.338\n   favstats.eu; @favstats   ") +
  theme(
    plot.title = element_text(size = 18, face = "bold", hjust = 0.5),
    plot.caption = element_text(size = 10),
    legend.justification = c(1, 0),
    legend.position = c(1, 0.1),
    legend.title = element_text(size = 10), 
    #axis.ticks.length = unit(3, "cm"),
    legend.direction = "vertical") +
  guides(fill = guide_colorbar(barwidth = 0.7, barheight = 10,
                title.position = "bottom", title.hjust = 0.5,
                label.theme = element_text(colour = "black", size = 9, angle = 0)))

countydata
```



## Analysis / Dataviz

```{r, analysis}
totalcensus::dict_cbsa #%>% 
              mutate(county_fips = paste0(STATE, COUNTY)) %>% 
              select(CBSA, central_outlying, county_fips)

elec2016_url<- "https://raw.githubusercontent.com/mkearney/presidential_election_county_results_2016/master/data/pres.elect16.results.2018.csv"
              
elec2016 <- readr::read_csv(elec2016_url)

elec2016 %>% 
  drop_na(county) %>% 
  filter(cand %in% c("Donald Trump", "Hillary Clinton")) %>% 
  rename(county_fips = fips) %>% 
  left_join(tariff_data) %>% 
  distinct(county_fips, .keep_all = T) %>% 
  mutate(share_export_retal = get_percentage(total_exports_under_retaliation_mil, total_exports_mil)) %>% 
  mutate(direct_jobs_retal = get_percentage(direct_export_supported_jobs_under_retaliation, direct_export_supported_jobs)) %>% 
  mutate(total_jobs_retal = get_percentage(total_export_supported_jobs_under_retaliation, total_export_supported_jobs)) %>% 
  mutate(cat_export_retal = cut(share_export_retal,  
                 breaks = c(0, 3, 6, 12, 20, 100), 
                 labels = c("0 - 3%", "3 - 6%", 
                          "6 - 12%", "12 - 20%", 
                            "20% and above"))) %>% 
  mutate(cat_jobs_retal = cut(total_jobs_retal,  
                 breaks = c(0, 3, 6, 12, 20, 100), 
                 labels = c("0 - 3%", "3 - 6%", 
                          "6 - 12%", "12 - 20%", 
                            "20% and above"))) %>% 
  drop_na(cat_jobs_retal) %>% 
  ggplot(aes(cat_jobs_retal, pct, color = cat_jobs_retal)) +
  # geom_violin(alpha = 0.6, fill = NA) +
  geom_boxplot(width = 0.2, fill = NA) +
  facet_wrap(~cand) +
  coord_flip() +
  theme_minimal() +
  theme(legend.position = "bottom")
  
ggsave_it(retalitory_total_exports, width = 14, height = 8)
```



## Conclusion

```{r}
library(Jeb)

jeb_meme <- jeb(country = "Brazil", level = 1)

plot(jeb_meme)
```

## F

```{r}
descr_data <- tidytemplate::load_it("data/descr_data.Rdata") 

descr_data

```

Note: Changes to County Data

https://www.economy.com/support/blog/buffet.aspx?did=50094FC4-C32C-4CCA-862A-264BC890E13B

Wade Hampton Census Area, Alaska (02-270)
Changed name and code to Kusilvak Census Area (02-158) effective July 1, 2015.

Oglala Lakota County, South Dakota (46-102)
Changed name and code from Shannon County (46-113) effective May 1, 2015.


```{r}
county_retaliation <-  tidytemplate::load_it("data/county_retaliation.Rdata") %>% 
  mutate(c_fips_lgc_ = ifelse(nchar(c_fips_lgc_) == 4, paste0(0, c_fips_lgc_), c_fips_lgc_))  %>% 
  mutate(c_fips_lgc_ = case_when(
    ## Wade Hampton Census Area changed to Kusilvak Census Area
    c_fips_lgc_ == "02270" ~ "02158",
    ## Shannon County to Oglala Lakota County
    c_fips_lgc_ == "46113" ~ "46102",
    ## Bedford + Bedford City changed to Bedford County
    c_fips_lgc_ == "51909" ~ "51019",
    T ~ c_fips_lgc_
  ))




bea_codes <- tidytemplate::load_it("data/bea_codes2.Rdata") %>% 
  mutate(bea_codes = as.character(bea_codes)) %>% 
  mutate(county_fips = as.character(county_fips)) %>% 
  select(bea_codes, county_fips)

beas <- county_retaliation %>% #filter(c_fips_lgc_ == "15901")
  inner_join(bea_codes, by = c("c_fips_lgc_" = "bea_codes")) %>% 
  select(-c_fips_lgc_)

elec2016_url<- "https://github.com/tonmcg/US_County_Level_Election_Results_08-16/raw/master/2016_US_County_Level_Presidential_Results.csv"
              
elec2016 <- readr::read_csv(elec2016_url) %>%  
  # filter(nchar(fips) != 2) %>% 
  # filter(cand %in% c("Donald Trump", "Hillary Clinton")) %>% 
  # filter(str_detect(state.name, "Alaska"))
  mutate(combined_fips = ifelse(nchar(combined_fips) == 4, paste0(0, combined_fips), combined_fips)) %>% 
  rename(county_fips = combined_fips) %>% 
  select(-county_name) %>% 
  mutate(county_fips = case_when(
    ## Wade Hampton Census Area changed to Kusilvak Census Area
    county_fips == "02270" ~ "02158",
    ## Shannon County to Oglala Lakota County
    county_fips == "46113" ~ "46102",
    ## Bedford + Bedford City changed to Bedford County
    county_fips == "51909" ~ "51019",
    T ~ county_fips
  ))

# GET("https://query.data.world/s/3eihaxlgaq35ttoq44jrisbzltcadm", write_disk(tf <- tempfile(fileext = ".xlsx")))
# readxl::read_excel(tf)
# 
# elec2016 <- read.xlsx(tf, sheetIndex = 4)
# 
# elec2016 <- elec2016 %>% 
#   clean_names() %>% 
#   mutate(county_fips = as.character(ansi_code)) 
```

```{r}
library(ggpmisc)

formula <- y ~ poly(x, 2, raw = TRUE)

county_retaliation %>% 
  rename(county_fips = c_fips_lgc_) %>%
  bind_rows(beas) %>% 
  inner_join(elec2016) %>%   
  mutate(voteshare = per_gop - per_dem) %>% 
  mutate(per_gop = 100 * per_gop) %>% 
  mutate(share_ret_xjd = 100 * share_ret_xjd) %>% 
  # ggplot(aes(voteshare)) +geom_histogram()
  ggplot(aes(per_gop, share_ret_xjd)) +
  geom_point(color = "darkgrey") +
  geom_smooth(method = "lm", formula = formula, color = "black") +
  stat_poly_eq(aes(label =  paste(..eq.label.., ..rr.label.., sep = "~~~~")),
               formula = formula, parse = TRUE, size = 5) +
  theme_minimal() +
  labs(x = "Trump Vote Share in %\n", y = "Share of total export-supported jobs under retaliation in %",
       title = "Trump Vote Share associated with Exposure to Retaliatory Tariffs",
       subtitle = "2017 Share of Export-Supported Jobs in Industries targeted by Partner's Retaliation by County Vote Share (%) in the 2016 U.S. presidential election\n",
       caption = "Source: Data compiled by Brookings (Census, BEA, BLS, IRS, EIA, Eurostat, Moody's Analytics,\nNAFSA, PIIE, Sabre, and Trade Map, International Trade Centre, www.intracen.org/marketanalysis)\n\nData Visualization by favstats.eu; @favstats") +
  theme(
    plot.title = element_text(size = 18, face = "bold"),
    plot.caption = element_text(size = 10),
    legend.justification = c(1, 0),
    legend.position = c(1, 0.1),
    legend.title = element_text(size = 10),
    axis.title = element_text(size = 12, face = "bold"),
    #axis.ticks.length = unit(3, "cm"),
    legend.direction = "vertical") 


ggsave_it(scatter_plot, width = 12, height = 8)
```


FIPS Modifications: 

https://apps.bea.gov/regional/xls/FIPSModifications.xlsx

```{r, fig.width=10, height = 8}

county_retaliation %>% 
  rename(county_fips = c_fips_lgc_) %>%
  bind_rows(beas) %>% 
  inner_join(elec2016) %>%
  mutate(trump_win = ifelse(per_gop >= .5, "Win", "Lost")) %>% 
  mutate(per_gop = 100 * per_gop) %>% 
  mutate(per_dem = 100 * per_dem) %>% 
  mutate(share_ret_xjd = 100 * share_ret_xjd) %>% 
  mutate(voteshare = per_gop - per_dem) %>% 
  # select(share_ret_xjd, voteshare, long, lat, group) %>%
  # gather(key, value, -long, -lat, -group) %>%
  # ggplot(aes(long, lat, group = group, fill = value)) +
  inner_join(urbnmapr::counties) %>% 
  ggplot(aes(long, lat, 
             group = group,
             # color = voteshare,
             fill = voteshare, 
             alpha = share_ret_xjd)) +
  # geom_hex(stat="identity", bins = 20, 
  #            color = "white",
  #            size = 0.05) +
  geom_polygon(color = "white", size = 0.05) +
  coord_equal() +
  theme_map() +
  # scale_color_gradient2(low = "#0015BC", mid = "lightgrey", high = "#E9141D") +
  scale_fill_gradient2("Trump Vote Share in %", low = "#0015BC", mid = "lightgrey", high = "#E9141D") +
  theme(
    plot.title = element_text(size = 18, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(size = 14, face = "italic", hjust = 0.5),
    plot.caption = element_text(size = 10),
    legend.justification = c(1, 0),
    legend.position = c(1, 0.1),
    legend.title = element_text(size = 10), 
    axis.ticks.length = unit(3, "cm"),
    # legend.direction = "vertical"
    )  +
  guides(fill = guide_colorbar(barwidth = 0.7, barheight = 10,
                title.position = "bottom", title.hjust = 0.5,
                label.theme = element_text(colour = "black", size = 9, angle = 0))) +
  labs(x = "", y = "",
       title = "Counties that voted for Trump most exposed to Retaliatory Tariffs",
       subtitle = "2017 Share of Export-Supported Jobs in Industries targeted by Partner's Retaliation\nby County Vote Share (%) in the 2016 U.S. presidential election",
       caption = "Source: Data compiled by Brookings (Census, BEA, BLS, IRS, EIA, Eurostat, Moody's Analytics,\nNAFSA, PIIE, Sabre, and Trade Map, International Trade Centre, www.intracen.org/marketanalysis)\n\nData Visualization by favstats.eu; @favstats")

ggsave_it(share_ret_xn_plot, width = 10, height = 10)
```


```{r}
bea_codes #%>%
  # anti_join(county_retaliation %>% 
  # rename(county_fips = c_fips_lgc_) )
  
county_retaliation %>% 
  # rename(county_fips = c_fips_lgc_) %>% 
  filter(s_name_lgc_lgs_ == "Hawaii") %>% 
  left_join(bea_codes, by = c("c_fips_lgc_" = "bea_codes"))

beas

library(rvest)

county_data <- read_html("https://en.wikipedia.org/wiki/User:Michael_J/County_table") %>% 
  # rvest::html_nodes("td") %>% 
  html_table() %>% 
  .[[1]] %>% 
  clean_names()

county_retaliation %>% 
  rename(county_fips = c_fips_lgc_) %>%
  bind_rows(beas) %>% 
  inner_join(elec2016) %>%
  mutate(per_gop = 100 * per_gop) %>% 
  mutate(per_dem = 100 * per_dem) %>% 
  mutate(share_ret_xjd = 100 * share_ret_xjd) %>% 
  mutate(voteshare = per_gop - per_dem) %>% 
  left_join(county_data %>%
     mutate(latitude = parse_number(latitude)) %>%
     mutate(longitude = -parse_number(longitude)) %>% 
     mutate(county_fips = ifelse(nchar(fips) == 4, paste0(0, fips), fips)) %>% 
     select(county_fips, latitude, longitude)
     ) %>% 
  arrange(desc(share_ret_xjd)) %>% 
  ggplot(aes(longitude, latitude)) +
  geom_hex() +
  theme_bw()
```


```{r}

urbnmapr::counties %>% 
  dplyr::left_join(beas) %>% 
  group_by(county_fips) %>% slice(1) 

county_retaliation %>% 
  rename(county_fips = c_fips_lgc_) %>%
  bind_rows(beas) %>% 
  full_join(urbnmapr::counties) %>% 
  left_join(elec2016) %>% 
  filter(is.na(votes_gop)) %>%
  filter(!is.na(long)) %>%
  group_by(county_fips) %>% slice(1) 


county_retaliation %>% 
  mutate(c_fips_lgc_ = ifelse(nchar(c_fips_lgc_) == 4, paste0(0, c_fips_lgc_), c_fips_lgc_) %>%
           as.character) %>%
  mutate(county_fips = as.character(c_fips_lgc_)) %>% 
  anti_join(urbnmapr::counties) %>% 
  arrange(c_name_lgc_) %>% 
  select(c_name_lgc_, county_fips, everything())  %>% 
  group_by(county_fips) %>% slice(1) 

urbnmapr::counties %>% 
  anti_join(county_retaliation %>% 
              mutate(county_fips = as.character(c_fips_lgc_)) %>%   
              mutate(county_fips = ifelse(nchar(county_fips) == 4, paste0(0, county_fips), county_fips) %>%
           as.character)) %>% 
  group_by(county_fips) %>% slice(1) %>% 
  arrange(county_name) %>% 
  select(county_name, county_fips, everything())


county_retaliation %>% 
  mutate(c_fips_lgc_ = ifelse(nchar(c_fips_lgc_) == 4, paste0(0, c_fips_lgc_), c_fips_lgc_) %>%
           as.character) %>% 
  anti_join(totalcensus::dict_fips %>% 
  mutate(c_fips_lgc_ = paste0(STATE, COUNTY)))  %>% 
  group_by(c_fips_lgc_) %>% slice(1) %>% 
  mutate(county_fips = c_fips_lgc_) %>% 
  inner_join(urbnmapr::counties)  %>% 
  ggplot(aes(long, lat, group = group, fill = share_ret_xn)) +
  geom_polygon(color = NA) +
  coord_map() +
  theme_map() 
```

```{r}
elec2016 %>% 
  # group_by(st) %>% slice(1)
  filter(str_detect(county_fips, "15009"))
```

```{r}
toilets <-
    read.csv("data/toilet.csv.csv",
             header = TRUE, stringsAsFactors = FALSE) %>%
    mutate(long = Longitude, lat = Latitude) %>%
    select(ToiletID, long, lat)

p <-
    ggplot(toilets, aes(x = long, y = lat)) +
    geom_hex() +
    coord_equal()

print(p)


county_retaliation %>% 
  rename(county_fips = c_fips_lgc_) %>%
  bind_rows(beas) %>% 
  inner_join(elec2016) %>%
  mutate(trump_win = ifelse(per_gop >= .5, "Win", "Lost")) %>% 
  mutate(per_gop = 100 * per_gop) %>% 
  mutate(per_dem = 100 * per_dem) %>% 
  mutate(share_ret_xjd = 100 * share_ret_xjd) %>% 
  mutate(voteshare = per_gop - per_dem) %>% 
  # select(share_ret_xjd, voteshare, long, lat, group) %>%
  # gather(key, value, -long, -lat, -group) %>%
  # ggplot(aes(long, lat, group = group, fill = value)) +
  inner_join(urbnmapr::counties) %>% 
  group_by(county_fips) %>% 
  summarise()
```

```{r}
pacman::p_load(geogrid, sf, tmap)

# input_file <- system.file("extdata", "london_LA.json", package = "geogrid")
# original_shapes <- st_read(input_file) %>% st_set_crs(27700)
# original_shapes$SNAME <- substr(original_shapes$NAME, 1, 4)


original_shapes <- st_read("https://github.com/jgoodall/us-maps/raw/master/geojson/county.geo.json") 

wi_details <- calculate_grid(original_shapes)
wi@data$xcentroid <- coordinates(wi)[,1]
wi@data$ycentroid <- coordinates(wi)[,2]
```

